Gesture Typing on Virtual Tabletop: Effect of Input on Performance

### 2017-08-22 paper.tex
add conclusion, and poster in poster directory

\numberofauthors{4}
% Notice how author names are alternately typesetted to appear ordered in 2-column format;
% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
% Actually, it's up to you to strictly adhere to this author notation.
\author{
  \alignauthor{
    \textbf{Antoine Loriette}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{antoine.loriette@gmail.com}
  }\alignauthor{
    \textbf{Sebastian Stein}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{author5@anotherco.com}
  }
  \vfil
  \alignauthor{
    \textbf{Roderick Murray-Smith}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{author2@anotherco.com}
  }\alignauthor{
    \textbf{John Williamson}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{jhw@dcs.gla.ac.uk}
  }
\vfil
}

@@

% =============================================================================
\section{Result}
% =============================================================================
The dependent variables are the success rate, the time taken per trial and the trace data when available. This allowed us to compute the dependent measure error rate defined as the percentage of unsucessful attempts as well as the text entry rate measured in Words Per Minute (WPM), as in [3], according to the following formula\footnote{$WPM = |T|/s \times 60/5$ where $|T|$ is the length of the transcribed string, s is time in seconds}.

@@

% % =============================================================================
% \section{Conclusion and Future work}
% % =============================================================================

% The user study showed that the users hit the accuracy ceiling when using a small surface. It also showed that the task behave according to Fitts law. The users seem to be limited by their ability to drive an indirect pointer rather than performing the difficulty of the task itself.

% These encouraging results open the way to testing the system with patients with spinal cord injury. More so, due to recent advance in hand pose recognition, the reality of interacting via touch through vision based system should be investigated further.

@@

% \balance
\bibliographystyle{acm-sigchi}
\bibliography{collection}

>>>>

\numberofauthors{4}
% Notice how author names are alternately typesetted to appear ordered in 2-column format;
% i.e., the first 4 autors on the first column and the other 4 auhors on the second column.
% Actually, it's up to you to strictly adhere to this author notation.
\author{
  \alignauthor{
    \textbf{Antoine Loriette}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{antoine.loriette@glasgow.ac.uk}
  }\alignauthor{
    \textbf{Sebastian Stein}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{sebastian.stein@glasgow.ac.uk}
  }
  \vfil
  \alignauthor{
    \textbf{Roderick Murray-Smith}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{rod@dcs.gla.ac.uk}
  }\alignauthor{
    \textbf{John Williamson}\\
    \affaddr{Dept. Computing Science}\\
    \affaddr{University of Glasgow}\\
    \affaddr{Scotland}\\
    \email{jhw@dcs.gla.ac.uk}
  }
\vfil
}

@@

% =============================================================================
\section{Result}
% =============================================================================
The dependent variables are the success rate, the time taken per trial and the trace data when available. This allowed us to compute the dependent measure error rate defined as the percentage of unsucessful attempts as well as the text entry rate measured in Words Per Minute (WPM), as in~\cite{Markussen2014}, according to the following formula\footnote{$WPM = |T|/s \times 60/5$ where $|T|$ is the length of the transcribed string, s is time in seconds}.

@@

% =============================================================================
\section{Conclusion}
% =============================================================================
We developed a system that affords gesture typing on arbitrary flat surfaces using depth camera tracking, and demonstrated a machine learning approach to the issue of detecting touch for fingertips which is effective for this mode of control. We designed an experiment with two research goals in mind. First, we compared the typing performance of our system against a control condition which was a direct interaction on a tablet. Second, we studied the influence of size and aspect ratio of the input surface on gesture typing performance. We showed that the participants could enter text at half the input rate and the same error rate on surface at least twice the size of the current visual feedback. We also showed that the input rate is largely independent of the surface size across the range of sizes we were able to examine. Gesture typing has promise for interaction outside of mobile devices (e.g. for motor impaired users who struggle with capacitive touch technologies). This paper indicates that while camera-tracked gesture typing performance is usable, input rates are lower than touchscreen performance, and this is not influenced by scaling of the input.

@@

\balance
\bibliographystyle{acm-sigchi}
\bibliography{collection}
